\chapter{Introduction}\label{ch:intro}
A blockchain can be defined as an immutable ledger maintained by a network of
mutually untrusting peers~\cite{And18}. Since the creation of Bitcoin (BTC) in January 2009
by the maverick Satoshi Nakamoto there has been an explosion of interest in
the underlying technology behind blockchains. Specifically, the
immutability and openness of the distributed ledger makes blockchain an
attractive option for markets with untrusting participants exposed to
information asymmetry. The market for carbon is particularly well suited to
the blockchain due to inconsistent government policy - for example the
ill-fated outcome of the Carbon Pollution Reduction Scheme in
Australia~\cite{Erg13}.

Recent attempts to create blockchain-based carbon markets have been met
with some success - but have been held back by technicalities or innovations
that disrupt the fundamental goal of using the blockchain as a
`trust machine'~\cite{EconT}.
I will outline how hydrogen certificates on the blockchain can be used to
automatically spend carbon tokens and add extra validation before being
sold on the commodity market. Hydrogen is particularly well-suited as an
example for certificate-based carbon markets due to hydrogen producers
attaching a carbon footprint to certificates.

I shall summarise how permissioned blockchains are principally useful for
carbon markets due to support for high-throughput transactions.
A carbon market would have to scale to a large number of distributed
producers with scalability matching hydrogen energy production -
an industry expected to be worth USD155 billion by 2022~\cite{Bru18}.
I will propose
Hyperledger Fabric as a blockchain framework - chiefly due to its support
for up to 3500 transactions per second (TPS) and a plugable consensus
algorithm~\cite{And18}.
Moreover, my proposed solution will accommodate an optional
carbon ‘reputation’ as part of the price for exchanging carbon tokens
between producers.

In Chapter~\ref{ch:intro} an overview of the thesis and its novel
approach to certificate-based carbon markets is presented.
In Chapter~\ref{ch:review} I outline the background to the project and
important literature for markets on a blockchain. In Chapter~\ref{ch:plan}
I provide methodology for the blockchain architecture.
In Chapter~\ref{ch:prep} I outline some preliminary results with
creating smart contracts (programs on the blockchain) for auctions on a
public blockchain. In Chapter~\ref{ch:conclusion} I conclude with some
remarks on the future potential for the thesis topic.


