\section{Introduction}
\begin{frame}{Problem}
    \begin{itemize}
        \item Hydrogen is a part of the Australian government's pivot towards
              clean energy.
              \begin{enumerate}[i]
                  \item \$540 million pledge for ``clean'' hydrogen.
                  \item Global market worth USD155 billion by 2022.
              \end{enumerate}
        \item Can an emissions trading scheme (ETS) be integrated into a
              blockchain with hydrogen certificates?
              \begin{enumerate}
                  \item Or more generally, for any energy certificate?
              \end{enumerate}
              \footnotetext[1]{Bruce S, Temminghoff M, Hayward J, Schmidt E,
                  Munnings C, Palfreyman D, Hartley P (2018)
                  National Hydrogen Roadmap. \textit{CSIRO}, Australia}
    \end{itemize}
\end{frame}

\begin{frame}{Hydrogen Energy}
    \begin{itemize}
        \item Hydrogen is a clean fuel that produces only water when consumed.
        \item Harvested from sources of renewable energy: solar and wind.
        \item Commonly harvested through natural gas reforming and a
              technique referred to as \textit{electrolysis}.
    \end{itemize}
\end{frame}

\begin{frame}{Aim}
    \begin{itemize}
        \item Is there a usable blockchain solution that will develop
              `trust' in an emissions trading scheme?
        \item \textit{Why?} Because customers are wary of centralised
              authorites with incosistent policy (e.g. Australia).
        \item \textit{How?} Using a permissioned blockchain to help
              develop trust without a centralised authority.
    \end{itemize}
\end{frame}