\section{Blockchain Performance}
\begin{frame}{System Performance}
    \begin{itemize}
        \item Although the aim of the thesis is not to produce the most
              high throughput carbon market - the performance of the
              system is still worth exploring.
        \item The performance of \textit{Fabric} has a tendency to
              suffer in the \textit{Validation Phase} of the transaction lifecycle.
        \item An observed tendency of Hyperledger is that as the transactions
              per second (TPS) increases, so do
              errors~\cite{10.1145/3448016.3452823}.
    \end{itemize}
\end{frame}
\subsection{Bottlenecks}
\begin{frame}{Common Bottlenecks}
    \begin{itemize}
        \item Multi-Version Concurrency Control (MVCC) - transactions in the
              same block updating the same key (transaction dependency).
        \item Phantom Read Conflicts - performing a read on a key range
              which has been updated.
              \begin{itemize}
                  \item For some reading range $i$ to $j$,
                        if a key has recently
                        been inserted then read a phantom read happens.
              \end{itemize}
    \end{itemize}
\end{frame}
\subsection{TPS Enhancements}
\begin{frame}{Enhancements to TPS}
    \begin{itemize}
        \item Represent assets on the blockchain as a sum of deltas to avoid
              MVCC errors.
        \item Example: CarbonCoin is the sum of deltas in Equation~\ref{eq:2}.
              \begin{itemize}
                  \item Each $\delta_i$ contains a unique combination of owner,
                        transaction identifier and sign.
                  \item Each $x_i$ represents the asset value (for example 500).
              \end{itemize}
        \item Localise the phantom read conflicts into `low TPS' domains.
    \end{itemize}
    \begin{equation}
        \text{Asset Value} = \delta_1 x_1 + \delta_2 x_2 + \dots + \delta_n x_n
        \label{eq:2}
    \end{equation}
\end{frame}